Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-23 sections/srfm.tex
tiny update

The principle of these methods is illustrated in
Fig.~\ref{fig:lm}. Initially, all fluorophores within the sample are
inactivated (``off''-state, grey dots in Fig.~\ref{fig:lm}a). After applying light suitable to switch the fluorophores
(cyan background, Fig.~\ref{fig:lm}b) from the inactivated to
the activated (``on'') state (white dots), the activated molecules are excited
(green background, yellow dots) and their emission is recorded. The excitation
light is applied as long as all excited molecules have bleached (black
dots). The series of activation, excitation and read-out is repeated until all
fluorophores have been excited and bleached, which results in a set of images
containing diffraction limited emission spots of all fluorophores in the
sample.

@@

This brief explanation is far from being exhaustive and does not consider the
differences in the implementations of the various techniques. An in-depth
overview is provided by several reviews of the techniques
\cite{Sengupta2014,Liu2015,Sauer2017}, suitable dyes \cite{Li2018a} as well
as by detailed imaging protocols \cite{Gould2009,Schermelleh2010,Linde2011}.
\subsubsection{Deterministic approaches}
\label{sec:deterministic-approaches}

@@

\subsection{General approach}

\subsubsection{Different approaches}
While the majority of SRFM techniques follows the approach outlined above,
other techniques exist that use different approaches.

\subsection{Scanning techniques}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:

>>>>

The principle of these methods is illustrated in
Fig.~\ref{fig:lm}. Initially, all fluorophores within the sample are
inactivated (``off''-state, grey dots in Fig.~\ref{fig:lm}a). Next,  light suitable to switch the fluorophores
(cyan background, Fig.~\ref{fig:lm}b) from the inactivated to
the activated (``on'') state (white dots) is applied. The intensity of the
activation light is selected such that only a small subset of the inactivated
molecules is activated, at maximum one molecule per area of the diffraction limited spot. The activated molecules are excited
(green background, yellow dots) and their emission is recorded. The excitation
light is applied as long as all excited molecules have bleached (black
dots). The series of activation, excitation and read-out is repeated until all
fluorophores have been excited and bleached, which results in a set of images
containing diffraction limited emission spots of all fluorophores in the
sample.

@@

This brief explanation is far from being exhaustive and does not consider the
differences in the implementations of the various techniques. An in-depth
overview is provided by several reviews of the techniques
\cite{Patterson2010,Sengupta2014,Liu2015,Sauer2017}, suitable dyes \cite{Li2018a} as well
as by detailed imaging protocols \cite{Gould2009,Schermelleh2010,Linde2011}.

\subsubsection{Deterministic approaches}
\label{sec:deterministic-approaches}

@@

% \subsection{General approach}

% \subsubsection{Different approaches}
% While the majority of SRFM techniques follows the approach outlined above,
% other techniques exist that use different approaches.

% \subsection{Scanning techniques}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
